Implementation of a stable, high-power optical lattice for quantum gas microscopy

### 2018-06-21 LatticeOptics/latticeOpticsv5/LatticeOpticsV5.tex
- decided for Sebastian's version of beam-monitoring section - revision of abstract - repositioning of figures for formatting

\date{\today}
\begin{abstract}
  We describe the design and implementation of a stable high-power \unit{1064}{nm} laser system to generate optical lattices for experiments with ultracold quantum gases. The system is based on a low-noise laser amplified by an array of four heavily modified, high-power fiber amplifiers. The beam intensity is stabilized and controlled with a nonlinear feedback loop. Using real-time monitoring of the resulting optical lattice, we demonstrate a shot-to-shot stability of the lattice position at 1.4\% of the lattice spacing and a long-term (six month) stability of 0.5\% RMS of the lattice spacing itself.
\end{abstract}
\maketitle

@@

\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.85\columnwidth]{Figure1.pdf}
    \caption{\textbf{High level overview} showing the major components of the lattice laser feedback system.}\label{fig:high_level}
  \end{center}
\end{figure}

>>>>

\date{\today}
\begin{abstract}
We describe the design and implementation of a stable high-power \unit{1064}{nm} laser system to generate optical lattices for experiments with ultracold quantum gases. The system is based on a low-noise laser amplified by an array of four heavily modified, high-power fiber amplifiers. The beam intensity is stabilized and controlled with a nonlinear feedback loop. 
%Using real-time monitoring of the resulting optical lattice, we demonstrate a shot-to-shot stability of the lattice position at 1.4\% of the lattice spacing and a long-term (six month) stability of 0.5\% RMS of the lattice spacing itself.
Using real-time monitoring of the resulting optical lattice, we find the stability of the lattice site positions to be well below the lattice spacing for several hours. The pointing stability of the optical lattice beams is around one lattice spacing and the long-term (six month) relative stability of the lattice spacing itself is 0.5\% RMS.
\end{abstract}
\maketitle

@@

\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.8\columnwidth]{Figure1.pdf}
    \caption{\textbf{High level overview} showing the major components of the lattice laser feedback system.}\label{fig:high_level}
  \end{center}
\end{figure}
